An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-13 poly-embed-journal/reviews/jmlr-response.tex
One final pass on edits

	See margin comment 1 in orange.

@@

	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo. 
\end{enumerate}

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
    See margin comment 3.

  \item \emph{Proposition 21 and upper bounding the original loss.}

@@

	The reviewer is correct that the paper is essentially restricted to the polyhedral setting.  (There are extensions beyond the polyhedral case in Section 6, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.

>>>>

	We have clarified this point with a concrete example; see margin comment 1 in orange.

@@

	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a  bit imprecise; we clarify that we are discussing $u \in \bigcup_{U \in \mathcal{U}} U$.
\end{enumerate}

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of \S~\ref{sec:top-k} (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
    See margin comment 3.

  \item \emph{Proposition~\ref{prop:embed-bayes-risks} and upper bounding the original loss.}

@@

	The reviewer is correct that the paper is essentially restricted to the polyhedral setting.  (There are extensions beyond the polyhedral case in \S~\ref{sec:min-rep-sets}, but not far beyond.)  Our goal is not to characterize the full set of consistent surrogates, but to provide a general framework for the design and analysis of polyhedral surrogate losses.
